---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
Sys.setenv(OPENSSL_CONF="/dev/null")
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

# oda-portfolio

The codes in this repository establish a pipeline with the [`{targets}`](https://books.ropensci.org/targets/) package
to calculated a number of biodiversity related indicators for all protected 
areas within countries that received official development aid by OECD member 
countries.

For this, the World Database on Protected Areas (WDPA) is downloaded and pre-processed
to correct invalid geometries. From the OECD data sharing platform, information
about which countries retrieved ODA is fetched. Additional countries to be included
in the analysis can be added by manually listing ISO3 codes in a new line in the 
file called [`additional_isos`](additional_isos). 

Indicators are calculated using [`mapme.pipelines`](https://github.com/mapme-initiative/mapme.pipelines).
The indicator configuration can be changed by adapting [`config.yaml`](config.yaml). 

High-level configuration, such as inputs, data directories and outputs can be
configured by adapting [`_targets.R`](_targets.R).

The pipeline currently consists of the following functionality:

- [`wdpa.R`](R/wdpa.R): fetching and pre-processing WDPA data
- [`oecd.R`](R/oecd.R): fetching OECD information and subletting WDPA to respective ISO3 codes
- [`mapme.R`](R/mapme.R): indicator calculation with [`mapme.pipelines`](https://github.com/mapme-initiative/mapme.pipelines)

To run the pipeline, issue the following command in a shell:

```shell
$ Rscript -e 'targets::tar_make()'
```

Together these routines establish the following pipeline:

```{r, results = "asis", echo = FALSE}
cat(c("```mermaid", targets::tar_mermaid(targets_only = TRUE), "```"), sep = "\n")
```



