---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
Sys.setenv(OPENSSL_CONF="/dev/null")
```

# oda-portfolio

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of oda-portfolio is to establish a pipeline with the `{targets}` package
to calculated indicators for all protected areas within countries that received
official development aid by OECD member countries.


```{r, results = "asis", echo = FALSE}
cat(c("```mermaid", targets::tar_mermaid(targets_only = TRUE), "```"), sep = "\n")
```

For this, ISO3 codes of ODA-receiving countries are retrieve from OECD 
servers. Additional ISO3 codes that should be included anyways, should be manually
added to `additional_isos`. 

To adjust the pipeline change the contents of `_targets.R` and `config.yaml` 
to your local settings and then run the following from a shell:

```shell
$ Rscript -e 'targets::tar_make()'
```
